\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.

\medskip
In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers growth. In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain} a).

>>>>

The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}. The mesh adapts within thee stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. In the simulations shown in this work, mesh will adapt as a response to oscillations in phase saturation field with prescribed interpolation error estimate.

\medskip
In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics. In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational domain is shown Fig.~\ref{fig:testcase_heter_domain} (a),
